Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-17 paper/paper.tex
update results again, this time slightly better

In Section~\ref{sec:algsel}, we discuss the features that are used to describe
instances, and we describe our algorithm selection approach. It combines a
presolving step, which allows us to easy instances very quickly, with the
algorithm selection approach \LLAMA~\cite{kotthoff_llama_2013}.
In Section~\ref{sec:algsel-exps}, we experimentally evaluate our selection
approach, and show that it is able to close more than 50\% of the gap between the
single best and the virtual best solver.
We conclude and give directions for future work in Section~\ref{sec:concs}.

@@

Table~\ref{tab:res} shows the performance of our algorithm selection approach, compared to two
baselines, on the reduced set of 2336 instances. The virtual best solver is the oracle predictor
that, for each instance, chooses the best solver from our portfolio. This is the upper bound of what
an algorithm selection approach can achieve. The single best solver is the one solver from the
portfolio that has the overall best performance across the entire set of instances, at the CPU time
limit of \SI{e8}{\ms}, i.e.\ \GlasgowTwo. We consider it a lower bound on the performance of the
algorithm selection approach.  We are able to solve 28 more instances than the single best solver
within the timeout, with only an additional 18 to the virtual best. In terms of average performance,
we are able to close more than \SI{50}{\percent} of the gap between the single best and the virtual
best solver.

@@

\begin{table}[p]
    \centering\setlength{\tabcolsep}{1em}
\begin{tabular}{lrrr}
  \toprule
model & mean MCP & solved instances & mean performance\\
  \midrule
virtual best & 0 & 2219 & 5822809\\
\LLAMA & 902316 & 2201 & 6726782\\
\GlasgowTwo & 1960992 & 2173 & 7783801\\
   \bottomrule \\
\end{tabular}
\caption{Algorithm selection performance on the reduced set of 2336 instances. MCP is the
misclassification penalty; that is, the additional time required to solve an instance because of
choosing solvers that perform worse than the best. Mean performance is over all instances; when an
instance is not solved, its performance is set to the time limit
(\SI{e8}{\ms}).}\label{tab:res}
\end{table}

@@

Table~\ref{tab:res} shows the performance of the selection model on its own. The performance of the
entire algorithm selection system, including the preprocessing, is shown in Table~\ref{tab:resfull}.
Our system is able to close more than \SI{50}{\percent} of the gap between
single and virtual best, similar to the results on the reduced set of instances.

@@

\begin{table}[p]
    \centering\setlength{\tabcolsep}{1em}
\begin{tabular}{lrrr}
  \toprule
model & mean MCP & solved instances & mean performance\\
  \midrule
virtual best & 0 & 5608 & 2375913\\
\LLAMA & 368176 & 5590 & 2744765\\
\GlasgowTwo & 798660 & 5562 & 3174573\\
   \bottomrule \\
\end{tabular}
\caption{Algorithm selection system performance on the full set of 5725
instances.}\label{tab:resfull}
\end{table}

>>>>

In Section~\ref{sec:algsel}, we discuss the features that are used to describe
instances, and we describe our algorithm selection approach. It combines a
presolving step, which allows us to easy instances very quickly, with the
algorithm selection approach \LLAMA~\cite{kotthoff_llama_2013}.
In Section~\ref{sec:algsel-exps}, we experimentally evaluate our selection
approach, and show that it is able to close more than \SI{60}{\percent} of the
gap between the single best and the virtual best solver. We conclude and give
directions for future work in Section~\ref{sec:concs}.

@@

Table~\ref{tab:res} shows the performance of our algorithm selection approach, compared to two
baselines, on the reduced set of 2336 instances. The virtual best solver is the oracle predictor
that, for each instance, chooses the best solver from our portfolio. This is the upper bound of what
an algorithm selection approach can achieve. The single best solver is the one solver from the
portfolio that has the overall best performance across the entire set of instances, at the CPU time
limit of \SI{e8}{\ms}, i.e.\ \GlasgowTwo. We consider it a lower bound on the performance of the
algorithm selection approach.  We are able to solve 30 more instances than the single best solver
within the timeout, with only an additional 16 to the virtual best. In terms of average performance,
we are able to close \SI{64}{\percent} of the gap between the single best and the virtual
best solver.

@@

\begin{table}[p]
    \centering\setlength{\tabcolsep}{1em}
\begin{tabular}{lrrr}
  \toprule
model & mean MCP & solved instances & mean performance\\
  \midrule
virtual best & 0 & 2219 & 5822809\\
\LLAMA & 705097 & 2203 & 6529563\\
\GlasgowTwo & 1960683 & 2173 & 7783492\\
   \bottomrule \\
\end{tabular}
\caption{Algorithm selection performance on the reduced set of 2336 instances. MCP is the
misclassification penalty; that is, the additional time required to solve an instance because of
choosing solvers that perform worse than the best. Mean performance is over all instances; when an
instance is not solved, its performance is set to the time limit
(\SI{e8}{\ms}).}\label{tab:res}
\end{table}

@@

Table~\ref{tab:res} shows the performance of the selection model on its own. The performance of the
entire algorithm selection system, including the preprocessing, is shown in Table~\ref{tab:resfull}.
Our system is able to close more than \SI{60}{\percent} of the gap between
single and virtual best, similar to the results on the reduced set of instances.

@@

\begin{table}[p]
    \centering\setlength{\tabcolsep}{1em}
\begin{tabular}{lrrr}
  \toprule
model & mean MCP & solved instances & mean performance\\
  \midrule
virtual best & 0 & 5608 & 2375913\\
\LLAMA & 287704 & 5592 & 2664293\\
\GlasgowTwo & 798660 & 5562 & 3174573\\
   \bottomrule \\
\end{tabular}
\caption{Algorithm selection system performance on the full set of 5725
instances.}\label{tab:resfull}
\end{table}
